### 2016-04-14 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Winter excluded!

#Run the model
lm2 <- lmer(RTL ~ Agemonths * (Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ)  + (1|FieldPeriodID) + (1|TerritoryID)+(1|PlateID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

@@

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1,
           col=Ageclass)) +
  ylab('Adult RTL') + 
  xlab('Juvenile RTL') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col='darkgrey')+
  annotate('text',x = 0,y = 2.1,label = 'A')

@@

Fig4B <- ggplot(temp2,
       aes(x = TimeDiff,
           y = Loss,
           colour=`Age (months)`,
           fill = `Age (months)`)) +
  ylab(expression(Delta*'RTL')) + 
  xlab('Time (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point(alpha=0)+
  stat_smooth(method = 'lm')+
  scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
    geom_abline(slope = 0,intercept = 0,lty = 2)+
  coord_cartesian(ylim = c(-0.5,0.3))+
  annotate('text',x = 0,y = 0.25,label = 'B')

@@

temp <- subset(Loss,Agemonths == 1)
#Run the model
lm2 <- lmer(Loss ~ (Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ) + (1|FieldPeriodID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

@@

Fig5B <- ggplot(temp,
       aes(x = Tarsus,
           y = Loss,
           col=Sex)) +
  ylab(expression(Delta*'RTL')) + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point()+
  stat_smooth(method = 'lm')+
  scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 19,y = 1.1,label = 'B')

>>>>

#Run the model
lm2 <- lmer(RTL ~ Agemonths*(Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ)  + (1|FieldPeriodID) + (1|TerritoryID)+(1|PlateID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

@@

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1,
           col=Ageclass)) +
  ylab('Adult RTL') + 
  xlab('Juvenile RTL') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point()+
  stat_smooth(method = 'lm')+
  annotate('text',x = 0,y = 2.1,label = 'A')

@@

Fig4B <- ggplot(temp2,
       aes(x = Ageclass,
           y = Loss)) +
  ylab(expression(Delta*'RTL')) + 
  xlab('Time (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(col = 'grey')+
  annotate('text',x = 0.5,y = 1.5,label = 'B')+
  geom_abline(slope = 0,intercept = 0,lty = 2)

@@

temp <- Loss
#Run the model
lm2 <- lmer(Loss ~ Agemonths*(Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ) + (1|FieldPeriodID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

@@

boxplot(Loss~Helper*Ageclass,data=Loss)

temp <- Loss

Fig5B <- ggplot(temp,
       aes(col = factor(Helper),
           y = Loss,
           x=Ageclass)) +
  ylab(expression(Delta*'RTL')) + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_boxplot(notch=T)+
  scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  scale_fill_manual(values = c('grey','darkorange','darkgreen'))
